### 2022-03-05 paper/output/document/thesis_4_applications.tex
chaper 5 cleaned
added will's fixes to ch5

%
\begin{isabellebody}%
\setisabellecontext{thesis{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}applications}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Applications \label{sec:applications}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this chapter, I use my system to produce sophisticated, nuanced
responses to two moral dilemmas. These dilemmas serve as examples of how my system could be used
in practice and demonstrate my system's ability to formalize longer, more complicted ethical arguments
than those presented in Chapter 3. 
Many of the tests in Section \ref{testing} perform metaethical reasoning, which analyzes properties
of morality itself and involves questions about the nature of ethical truth. In this chapter, I perform
``applied ethical reasoning," which is the use of ethics to resolve dilemmas and make judgements about 
what an agent should or should not do. This is the kind of reasoning necessary for an AI agent using my system to
navigate the real world.

@@

This account not only describes the kind of maxims that fail or pass the universalizability test, but it 
also provides a guide to constructing permissible maxims about uttering falsehoods. As an example, 
consider the idea of throwing a surprise birthday party. At first glance, the maxim of action is 
something like, ``When it is my friend's birthday, I will secretly plan a party so that I can surprise
them.'' The goal ``so that I can surprise them'' clearly requires that your friend believe the falsehood that 
you are not planning a party, else the surprise would be ruined. This seems to imply that 
Kantian ethics would prohibit surprise parties, which is a sad conclusion for birthday-lovers everywhere. 
Knowing that this maxim is prohibited because the goal requires belief
in a falsehood provides a way to rescue surprise parties. When throwing a 
surprise party, the objective is \emph{not} to surprise your friend, but to celebrate
your friend and help them have a fun birthday. If someone ruins the surprise, but the party is still fun
and the birthday person feels loved, then such a party is a success! Someone who
calls this party a failure is clearly missing the point of a surprise party. The goal of 
a surprise party is not the surprise itself, but rather celebrating the birthday person. The modified
goal no longer requires belief in the falsehood and thus passes the universalizability test.

@@

%:%90=56%:%
%:%102=59%:%
%:%103=60%:%

@@

%:%125=83%:%
%:%126=83%:%
%:%128=84%:%
%:%129=85%:%

@@

%:%133=89%:%
%:%134=90%:%

@@

%:%141=98%:%
%:%142=98%:%
%:%144=99%:%
%:%145=100%:%
%:%146=100%:%
%:%147=101%:%
%:%148=101%:%
%:%149=102%:%
%:%151=103%:%
%:%152=103%:%
%:%153=104%:%
%:%154=104%:%
%:%155=105%:%
%:%157=106%:%
%:%158=107%:%

@@

%:%164=114%:%
%:%165=115%:%

@@

@@

%:%176=125%:%
%:%177=126%:%
%:%179=127%:%
%:%182=129%:%
%:%183=130%:%

@@

@@

%:%197=143%:%
%:%199=144%:%
%:%200=145%:%

@@

%:%202=146%:%
%:%203=147%:%
%:%204=147%:%
%:%206=148%:%
%:%207=149%:%
%:%208=149%:%
%:%209=150%:%
%:%210=150%:%
%:%212=151%:%
%:%215=153%:%
%:%216=154%:%

@@

@@

%:%221=158%:%
%:%222=159%:%

@@

%:%225=161%:%
%:%226=161%:%
%:%227=162%:%
%:%229=163%:%
%:%230=164%:%
%:%231=164%:%
%:%232=165%:%
%:%234=166%:%
%:%235=167%:%

@@

%:%240=171%:%
%:%241=172%:%
%:%243=173%:%
%:%244=173%:%
%:%245=174%:%
%:%252=175%:%
%:%253=175%:%
%:%254=176%:%
%:%255=176%:%
%:%256=177%:%
%:%257=177%:%
%:%259=178%:%
%:%260=179%:%

@@

%:%263=181%:%
%:%264=182%:%
%:%265=182%:%
%:%266=183%:%
%:%267=183%:%
%:%268=184%:%
%:%269=184%:%
%:%270=185%:%
%:%271=185%:%
%:%272=185%:%
%:%274=186%:%
%:%275=187%:%
%:%276=187%:%
%:%277=188%:%
%:%287=190%:%
%:%288=191%:%

@@

@@

%:%303=205%:%
%:%304=206%:%
%:%306=207%:%
%:%307=208%:%
%:%310=210%:%
%:%311=211%:%

@@

@@

%:%321=220%:%
%:%322=221%:%

@@

%:%325=223%:%
%:%326=223%:%
%:%327=224%:%
%:%329=225%:%
%:%330=226%:%
%:%331=226%:%
%:%332=227%:%
%:%334=228%:%
%:%335=228%:%
%:%336=229%:%
%:%338=230%:%
%:%339=230%:%
%:%340=231%:%
%:%343=232%:%
%:%347=232%:%
%:%348=232%:%
%:%350=233%:%
%:%351=234%:%

@@

%:%364=240%:%
%:%365=241%:%

@@

%:%411=281%:%
%:%423=284%:%
%:%424=285%:%
%:%425=286%:%
%:%426=287%:%
%:%427=288%:%
%:%428=289%:%
%:%429=290%:%
%:%430=291%:%

@@

@@

%:%443=303%:%
%:%445=304%:%
%:%446=304%:%
%:%447=305%:%
%:%448=305%:%
%:%450=306%:%
%:%451=307%:%
%:%452=308%:%
%:%453=308%:%
%:%454=309%:%
%:%455=309%:%
%:%457=310%:%
%:%458=310%:%
%:%459=311%:%
%:%460=311%:%
%:%462=312%:%
%:%463=312%:%
%:%464=313%:%
%:%465=313%:%
%:%466=314%:%
%:%468=315%:%
%:%469=316%:%
%:%472=318%:%
%:%473=319%:%
%:%474=320%:%
%:%475=321%:%
%:%477=323%:%
%:%478=323%:%
%:%480=324%:%
%:%481=324%:%
%:%482=325%:%
%:%483=325%:%
%:%484=326%:%
%:%486=327%:%
%:%487=327%:%
%:%488=328%:%
%:%489=328%:%
%:%491=329%:%
%:%492=329%:%
%:%493=330%:%
%:%494=330%:%
%:%495=331%:%
%:%497=332%:%
%:%498=333%:%
%:%514=365%:%
%:%515=366%:%
%:%516=367%:%
%:%517=368%:%
%:%518=369%:%
%:%519=370%:%
%:%520=371%:%
%:%521=372%:%

@@

@@

%:%525=375%:%
%:%526=376%:%
%:%527=377%:%
%:%529=378%:%
%:%530=378%:%
%:%531=379%:%
%:%533=380%:%
%:%534=380%:%
%:%535=381%:%
%:%537=382%:%
%:%538=383%:%
%:%539=384%:%
%:%540=385%:%
%:%541=386%:%
%:%542=386%:%
%:%543=387%:%
%:%545=388%:%
%:%546=389%:%
%:%547=390%:%
%:%548=391%:%
%:%549=392%:%
%:%550=393%:%
%:%551=394%:%
%:%552=394%:%
%:%553=395%:%
%:%555=396%:%
%:%556=397%:%
%:%557=397%:%
%:%558=398%:%
%:%561=399%:%
%:%565=399%:%
%:%566=399%:%
%:%567=399%:%
%:%569=400%:%
%:%570=401%:%
%:%571=402%:%
%:%581=404%:%
%:%582=405%:%
%:%583=406%:%
%:%584=407%:%
%:%586=409%:%
%:%587=409%:%
%:%588=410%:%
%:%590=411%:%
%:%591=411%:%
%:%592=412%:%
%:%594=413%:%
%:%595=413%:%
%:%596=414%:%
%:%598=415%:%
%:%599=415%:%
%:%600=416%:%
%:%602=417%:%
%:%603=417%:%
%:%604=418%:%
%:%606=419%:%
%:%607=420%:%
%:%608=420%:%
%:%609=421%:%
%:%616=422%:%
%:%617=422%:%
%:%618=423%:%
%:%619=423%:%
%:%620=424%:%
%:%621=424%:%
%:%622=424%:%
%:%623=425%:%
%:%624=425%:%
%:%625=426%:%
%:%626=426%:%
%:%627=426%:%
%:%628=427%:%
%:%629=427%:%
%:%630=428%:%
%:%631=428%:%
%:%632=428%:%
%:%633=429%:%
%:%643=431%:%
%:%644=432%:%
%:%645=433%:%
%:%646=434%:%
%:%647=435%:%
%:%648=436%:%
%:%649=437%:%
%:%650=438%:%

@@

>>>>

%
\begin{isabellebody}%
\setisabellecontext{thesis{\isacharunderscore}{\isadigit{4}}{\isacharunderscore}applications}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\isadelimdocument
%
\endisadelimdocument
%
\isatagdocument
%
\isamarkupsection{Applications \label{applications}%
}
\isamarkuptrue%
%
\endisatagdocument
{\isafolddocument}%
%
\isadelimdocument
%
\endisadelimdocument
%
\begin{isamarkuptext}%
In this chapter, I demonstrate that my system can produce correct judgements on challenging moral 
dilemmas that naive ethical reasoning cannot satisfactorily handle. My system can reproduce complex
ethical judgements because it is faithful to philosophical literature.
These dilemmas serve as examples of how my system could be used
in practice and demonstrate my system's ability to formalize longer, more complicted ethical arguments
than those presented in Chapter \ref{details}. 
Many of the tests in Section \ref{testing} perform metaethical reasoning, which analyzes properties
of morality itself and involves questions about the nature of ethical truth. In this chapter, I perform
``applied ethical reasoning," which is the use of ethics to resolve dilemmas and make judgements about 
what an agent should or should not do. This is the kind of reasoning necessary for an AI agent using my system to
navigate the real world.

@@

This account not only describes the kind of maxims that fail or pass the universalizability test, but it 
also provides a guide to constructing permissible maxims about uttering falsehoods. As an example, 
consider the idea of throwing a surprise birthday party. At first glance, the maxim of action is 
something like, ``When it is my friend's birthday, I will secretly plan a party so that I can surprise
them.'' The goal ``so that I can surprise them'' clearly requires that your friend believe the falsehood that 
you are not planning a party, else the surprise would be ruined. This seems to imply that 
Kantian ethics would prohibit surprise parties, which is a sad conclusion for birthday-lovers everywhere. 
Knowing that this maxim is prohibited because the goal requires belief
in a falsehood provides a way to rescue surprise parties. When throwing a 
surprise party, the objective is \emph{not} to surprise your friend, but to celebrate
your friend and help them have a fun birthday. If someone ruins the surprise, but the party is still fun
and the birthday person feels loved, then such a party is a success! Someone who
calls this party a failure is clearly missing the point of a surprise party. The goal of 
a surprise party is not the surprise itself, but rather celebrating the birthday person. The modified
goal\footnote{Some may worry that this argument implies that the ``means justify the ends,'' or that modifying
an act's goal can change its moral worth. This conclusion is not only unsurprising to Kantians, but it is the
defining feature of their theory. Under Kantian ethics, an action alone is not the kind of thing that can 
be moral or immoral; rather, a maxim, or a circumstances, act, goal tuple, is what has moral worth. The rightness 
of an action can hinge on the maxim's goal, circumstances, or act because these three features
of an action are inseparable.} no longer requires belief in the falsehood and thus passes the 
universalizability test.

@@

%:%82=54%:%
%:%83=55%:%
%:%92=58%:%

@@

%:%124=81%:%
%:%125=82%:%
%:%127=85%:%
%:%128=85%:%

@@

%:%131=87%:%
%:%132=88%:%

@@

%:%140=96%:%
%:%141=97%:%
%:%143=100%:%
%:%144=100%:%
%:%146=101%:%
%:%147=102%:%
%:%148=102%:%
%:%149=103%:%
%:%150=103%:%
%:%151=104%:%
%:%153=105%:%
%:%154=105%:%
%:%155=106%:%
%:%156=106%:%
%:%157=107%:%

@@

%:%162=111%:%
%:%163=112%:%

@@

%:%174=124%:%

@@

%:%177=127%:%
%:%178=127%:%
%:%179=128%:%
%:%181=129%:%

@@

%:%195=142%:%

@@

%:%198=145%:%
%:%199=145%:%

@@

%:%202=147%:%
%:%203=148%:%
%:%204=148%:%
%:%205=149%:%
%:%206=149%:%
%:%208=150%:%
%:%209=151%:%
%:%210=151%:%
%:%211=152%:%
%:%212=152%:%
%:%214=153%:%

@@

%:%219=157%:%

@@

%:%222=160%:%

@@

%:%224=161%:%
%:%225=162%:%
%:%227=163%:%
%:%228=163%:%
%:%229=164%:%
%:%231=165%:%
%:%232=166%:%
%:%233=166%:%
%:%234=167%:%

@@

%:%240=172%:%
%:%241=173%:%
%:%242=173%:%
%:%243=174%:%
%:%245=175%:%
%:%246=175%:%
%:%247=176%:%
%:%254=177%:%
%:%255=177%:%
%:%256=178%:%
%:%257=178%:%
%:%258=179%:%
%:%259=179%:%

@@

%:%263=182%:%
%:%264=183%:%
%:%265=183%:%
%:%266=184%:%
%:%267=184%:%
%:%268=185%:%
%:%269=185%:%
%:%270=186%:%
%:%271=186%:%
%:%272=187%:%
%:%273=187%:%
%:%274=187%:%
%:%276=188%:%
%:%277=189%:%
%:%278=189%:%
%:%279=190%:%

@@

%:%301=204%:%

@@

%:%304=207%:%
%:%305=207%:%
%:%306=208%:%
%:%308=209%:%
%:%309=210%:%

@@

%:%319=219%:%

@@

%:%322=222%:%

@@

%:%324=223%:%
%:%325=224%:%
%:%327=225%:%
%:%328=225%:%
%:%329=226%:%
%:%331=227%:%
%:%332=228%:%
%:%333=228%:%
%:%334=229%:%
%:%336=230%:%
%:%337=230%:%
%:%338=231%:%
%:%340=232%:%
%:%341=232%:%
%:%342=233%:%
%:%345=234%:%
%:%349=234%:%
%:%350=234%:%

@@

%:%355=238%:%
%:%356=239%:%

@@

%:%403=279%:%
%:%404=280%:%
%:%405=281%:%
%:%406=282%:%
%:%407=283%:%
%:%408=284%:%
%:%409=285%:%
%:%410=286%:%
%:%419=289%:%

@@

%:%441=302%:%

@@

%:%443=304%:%
%:%444=305%:%
%:%445=306%:%
%:%446=307%:%
%:%447=308%:%
%:%448=309%:%
%:%450=311%:%
%:%451=311%:%
%:%453=312%:%
%:%454=312%:%
%:%455=313%:%
%:%456=313%:%
%:%458=314%:%
%:%459=315%:%
%:%460=316%:%
%:%461=316%:%
%:%462=317%:%
%:%463=317%:%
%:%465=318%:%
%:%466=318%:%
%:%467=319%:%
%:%468=319%:%
%:%470=320%:%
%:%471=320%:%
%:%472=321%:%
%:%473=321%:%
%:%474=322%:%
%:%476=323%:%
%:%477=324%:%
%:%480=326%:%
%:%481=327%:%
%:%482=328%:%
%:%483=329%:%
%:%485=331%:%
%:%486=331%:%
%:%488=332%:%
%:%489=332%:%
%:%490=333%:%
%:%491=333%:%
%:%492=334%:%
%:%494=335%:%
%:%495=335%:%
%:%496=336%:%
%:%497=336%:%
%:%499=337%:%
%:%500=337%:%
%:%501=338%:%
%:%502=338%:%
%:%503=339%:%
%:%505=340%:%
%:%506=341%:%

@@

%:%523=374%:%

@@

%:%525=376%:%
%:%526=377%:%
%:%527=378%:%
%:%528=379%:%
%:%529=380%:%
%:%530=381%:%
%:%532=383%:%
%:%533=383%:%
%:%534=384%:%
%:%535=385%:%
%:%537=386%:%
%:%538=386%:%
%:%539=387%:%
%:%541=388%:%
%:%542=388%:%
%:%543=389%:%
%:%545=390%:%
%:%546=391%:%
%:%547=392%:%
%:%548=393%:%
%:%549=394%:%
%:%550=394%:%
%:%551=395%:%
%:%553=396%:%
%:%554=397%:%
%:%555=398%:%
%:%556=399%:%
%:%557=400%:%
%:%558=401%:%
%:%559=402%:%
%:%560=402%:%
%:%561=403%:%
%:%563=404%:%
%:%564=405%:%
%:%565=405%:%
%:%566=406%:%
%:%569=407%:%
%:%573=407%:%
%:%574=407%:%
%:%575=407%:%
%:%577=408%:%
%:%578=409%:%
%:%579=410%:%
%:%589=412%:%
%:%590=413%:%
%:%591=414%:%
%:%592=415%:%
%:%594=417%:%
%:%595=417%:%
%:%596=418%:%
%:%598=419%:%
%:%599=419%:%
%:%600=420%:%
%:%602=421%:%
%:%603=421%:%
%:%604=422%:%
%:%606=423%:%
%:%607=423%:%
%:%608=424%:%
%:%610=425%:%
%:%611=425%:%
%:%612=426%:%
%:%614=427%:%
%:%615=428%:%
%:%616=428%:%
%:%617=429%:%
%:%624=430%:%
%:%625=430%:%
%:%626=431%:%
%:%627=431%:%
%:%628=432%:%
%:%629=432%:%
%:%630=432%:%
%:%631=433%:%
%:%632=433%:%
%:%633=434%:%
%:%634=434%:%
%:%635=434%:%
%:%636=435%:%
%:%637=435%:%
%:%638=436%:%
%:%639=436%:%
%:%640=436%:%
%:%641=437%:%

@@

%:%679=467%:%
%:%680=468%:%
%:%681=469%:%
%:%682=470%:%
%:%683=471%:%
%:%684=472%:%
%:%685=473%:%
%:%686=474%:%
